### 2020-06-06 5_evaluation.tex
Tweak wording and space.

There are two points of interest on each ``limit 50\%'' curve: the point
where it intersects ``actual'' and the point where it intersects an
ideal scaling curve, computed by taking the initial time to solution
and assuming linear scaling. These points are marked for Charm++ in
Figure~\ref{fig:strong-scaling} with a black square and black circle,
respectively. Notably, the intersection between ideal and ``limit 50\%''
requires only a single node run, along with measurements of METG(50\%)
at each node count. Using this data it is possible to predict the
strong scalability of the code: i.e., the smallest time to solution,
and the number of nodes at which that time is achieved, while
maintaining at least 50\% efficiency. In
Figure~\ref{fig:strong-scaling} this can be seen as the distance
between the black square and circle; these are separated by a factor of
$1.22\times$ in node count, and $1.27\times$ in time to solution.

>>>>

There are two points of interest on each ``limit 50\%'' curve: the point
where it intersects ``actual'' and the point where it intersects an
ideal scaling curve, computed by taking the initial time to solution
and assuming linear scaling. These points are marked for Charm++ in
Figure~\ref{fig:strong-scaling} with a black square and black circle,
respectively.
Compared with brute-force benchmarking of an application at various
scales, the METG(50\%) measurements allow a single run of the
application at small scale to be used to estimate the strong scalability
of the code:
%% Notably, computing the ideal scaling line requires only
%% the running time on a single node, so the intersection between ideal
%% and ``limit'' can be found with only the single-node time to
%% solution, along with measurements of METG(50\%) at each node
%% count. Using this data it is possible to predict the
%% strong scalability of the code:
i.e., the smallest time to solution,
and the number of nodes at which that time is achieved, while
maintaining at least 50\% efficiency. In
Figure~\ref{fig:strong-scaling} this can be seen as the distance
between the black square and circle; these are separated by a factor of
$1.22\times$ in node count, and $1.27\times$ in time to solution.

### 2020-06-06 6_related.tex
Revert "Un-itemize the bulleted lists in sections 7 and 8."
This reverts commit b75938db0edc33113608b01a9966f9370966d97a.
Tweak wording and space.

Though smaller than full applications, mini-apps can be challenging to
implement to a level of quality sufficient for conducting comparative
studies between programming systems. {\color{blue} The largest studies
we know of consider at most 7 and 6 programming systems,
respectively~\cite{LULESH13, Deakin19}, and the latter only considers
on-node programming models.} In both cases, the mini-apps under study
require a separate, tuned implementation (in contrast to Task
Bench). Other studies usually lack a comprehensive evaluation, even if
multiple implementations are available:
(a) The PENNANT reference implementation supports
MPI/OpenMP/MPI+OpenMP~\cite{PENNANT}. A follow-up paper presents a
Regent implementation~\cite{Regent15}.
(b) One follow-up paper for the mini-app CoMD describes a Chapel
implementation~\cite{CoMDChapel16} (comparison against reference
only). Additional follow-up papers consider aspects of the reference
implementation only~\cite{CoMDLoadImbalance17,
  CoMDThreadedModels14}.
(c) A report on the Mantevo project~\cite{Mantevo09} describes a number of
mini-apps, but only includes self-comparisons based on reference
implementations.
And (d) A report on MiniAero~\cite{SandiaReportManyTaskRuntimes15} describes
four implementations of the mini-app, but only includes performance
results for three, and of those three only two can be compared in an
apples-to-apples manner as the last implementation uses a structured
rather than an unstructured mesh. A follow-up paper describes another
implementation in Regent~\cite{Regent15} (comparison against reference
only).

>>>>

Though smaller than full applications, mini-apps can be challenging to
implement to a level of quality sufficient for conducting comparative
studies between programming systems. {\color{blue} The largest studies
we know of consider at most 7 and 6 programming systems,
respectively~\cite{LULESH13, Deakin19}, and the latter only considers
on-node programming models.} In both cases, the mini-apps under study
require a separate, tuned implementation (in contrast to Task
Bench). Other studies usually lack a comprehensive evaluation, even if
multiple implementations are available:
(a) The PENNANT reference implementation supports
MPI/OpenMP/MPI+OpenMP~\cite{PENNANT}. A follow-up paper presents a
Regent implementation~\cite{Regent15}.
(b) One follow-up paper for the mini-app CoMD describes a Chapel
implementation~\cite{CoMDChapel16} (comparison against reference
only). Additional follow-up papers consider aspects of the reference
implementation only~\cite{CoMDLoadImbalance17,
  CoMDThreadedModels14}.
(c) A report on the Mantevo project~\cite{Mantevo09} describes a number of
mini-apps, but only includes self-comparisons based on reference
implementations.
And (d) A report on MiniAero~\cite{SandiaReportManyTaskRuntimes15} describes
four implementations of the mini-app, but only includes performance
results for three, of which only two can be compared in an
apples-to-apples manner as the last implementation uses structured
rather than unstructured meshes. A follow-up describes another
implementation in Regent~\cite{Regent15} (comparison vs.~reference
only).

### 2020-06-06 7_conclusion.tex
Revert "Un-itemize the bulleted lists in sections 7 and 8."
This reverts commit b75938db0edc33113608b01a9966f9370966d97a.
Tweak wording and space.

Task Bench is a new approach for evaluating the performance of
parallel and distributed programming systems. By separating the
specification of a benchmark from implementations in various
programming systems, Task Bench reduces overall developer effort to
$\mathcal{O}(m + n)$ (for $m$ benchmarks on $n$ systems) rather than
$\mathcal{O}(mn)$ as has been the case for all previous
benchmarks that we know of. This has enabled us to explore a broad space of
application scenarios and to do so with a large number of programming
systems. Our experiments have enabled the following
insights:
(1) METG for current distributed programming systems varies by over
  5 orders of magnitude.  Clearly understanding the needed task
  granularity is an important consideration in choosing a programming
  system for a new application.
(2) While some systems support METG(50\%) as small as 390~ns, this applies only to trivial dependencies and small CPU-based clusters. A number of factors (nontrivial dependencies, accelerators and cluster sizes in the hundreds of nodes) raise
  the METGs that can be achieved by over an order of magnitude: 100~\textmu{}s is a reasonable bound for most applications running at scale with current technologies.
(3) Systems that support asynchronous execution show benefits under
  balanced computation
  and communication, and load imbalance. However, these gains can be nullified by
  high baseline overheads.
(4) Systems for large scale data analysis require very large tasks
  (tens of seconds) to scale beyond small node counts,
  reflecting the very coarse tasks and lack of need for strong scaling
  performance in current workloads.
And (5) Task Bench has proven effective in finding performance issues
  and has lead to substantial improvements in several of the systems
  we study.

>>>>

Task Bench is a new approach for evaluating the performance of
parallel and distributed programming systems. By separating the
specification of a benchmark from implementations in various
programming systems, Task Bench reduces overall developer effort to
$\mathcal{O}(m + n)$ (for $m$ benchmarks on $n$ systems) rather than
$\mathcal{O}(mn)$ as has been the case for all previous
benchmarks that we know of. This has enabled us to explore a broad space of
application scenarios and to do so with a large number of programming
systems. Our experiments have enabled the following
insights:
(1) METG for current distributed programming systems varies by over
  5 orders of magnitude.  Clearly understanding the needed task
  granularity is an important consideration in choosing a programming
  system for a new application.
(2) While some systems support METG(50\%) as small as 390~ns, this applies only to trivial dependencies and small CPU-based clusters. A number of factors (nontrivial dependencies, accelerators and cluster sizes in the hundreds of nodes) raise
  the METGs that can be achieved by over an order of magnitude: 100~\textmu{}s is a reasonable bound for most applications running at scale with current technologies.
(3) Systems that support asynchronous execution show benefits under
  balanced computation
  and communication, and load imbalance. However, these gains can be nullified by
  high baseline overheads.
(4) Systems for large scale data analysis require very large tasks
  (tens of seconds) to scale beyond small node counts,
  reflecting the very coarse tasks and lack of need for strong scaling
  in current workloads.
And (5) Task Bench has proven effective in finding performance issues
  and has lead to substantial improvements in several systems
  we study.
